Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-09-11 paper/main.tex

In many practical optimization problems, the objective function is not
explicitly available and solutions are evaluated by means of expensive
prediction models, simulations or physical experiments. When decision variables
are continuous, the use of Bayesian surrogate-models, e.g., Gaussian processes,
in optimization has become
widespread~\citep{JonSchWel98go,ForKea2009surrogate}. Motivated by this
success, there have been attempts at adapting such surrogate models to the
combinatorial case~\citep{ZaeStoBar2014:ppsn,ZaeStoFriFisNauBar2014}.

@@

\citet{ZaeStoBar2014:ppsn,ZaeStoFriFisNauBar2014}
\citet{PerLopStu2015si}

@@

\newcommand{\FEmax}{\ensuremath{FE_{\max}}}

>>>>

In many practical optimization problems, the objective function is not
explicitly available and solutions are evaluated by means of expensive
prediction models, simulations or physical experiments. When decision variables
are continuous, the use of Bayesian surrogate-models, e.g., Gaussian processes,
in optimization has become
widespread~\citep{JonSchWel98go,ForKea2009surrogate}. Motivated by this
success, there have been attempts at adapting such Bayesian optimization
algorithms to the combinatorial case, a notable example being Combinatorial
Efficient Global Optimization
(CEGO)~\citep{ZaeStoBar2014:ppsn,ZaeStoFriFisNauBar2014}. However, the
ruggedness of combinatorial landscapes, which makes local search particularly
effective in the white-box context, lessens the effectiveness of global
surrogate models~\citep{EriPeaGar2019scalable}. Moreover, surrogate models are
expensive to train and optimize. Unless each function evaluation requires a day
or more, the time required by the Bayesian optimizer itself may impose a
significant overhead in computation time. \citet{PerLopStu2015si} recently
showed that ant colony optimization (ACO)~\citep{DorStu2004:book} is
competitive with CEGO on a black-box version of the travelling salesman problem
under a budget of $1\,000$ function evaluations. ACO basically builds a
probability distribution model from which solutions are sampled with a bias
towards the best solutions evaluated so far. As such, ACO may be considered a
type of estimation-of-distribution algorithm (EDA) for combinatorial
optimization.

In this work, we propose and analyze uMM, an EDA specifically designed for
black-box combinatorial optimization under a limited budget. The proposed uMM \ldots\MANUEL{what is the inspiration}
\

@@

@@

\newcommand{\FEmax}{\ensuremath{\textit{FE}_{\max}}}
